---
title: "Economic Connectedness"
format: html
author: Luke Li
execute:
    echo: false
---

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(primer.data)
```

## GRAPH 1

```{r}
#| message: false
connectedness |>
  drop_na() |>
  ggplot(aes(x = population)) + 
    geom_histogram(bins = 100, fill = "black", color = "white") + 
    scale_x_log10(labels = scales::comma_format()) +
    labs(title = "US County Popoulation Distribution 2018", 
  subtitle = "Popoulations are heavily skewed right, x-axis uses log scale", 
  x = "County Population", 
  y = "Number of Counties",
  caption = "Opportunity Insights")
```

Plot 1: US County Population Distribution (2018)
This histogram visualizes the distribution of county populations in the United States for the year 2018. It uses:

100 bins to show detailed variation.

A logarithmic x-axis (scale_x_log10) to handle the extreme right skew in population sizes (i.e., a small number of counties have very large populations).

Black-filled bars with white borders for high contrast.

Interpretation:
The plot reveals that most U.S. counties have relatively small populations, while a few are extremely populous. The log scale makes the skewness more interpretable by compressing the wide range of values.

## GRAPH 2

```{r}
#| message: false
connectedness |>
    drop_na() |> 
    ggplot(aes(x = population, y = connectedness)) + 
    geom_point(alpha = 0.3, fill = "black", color = "black", stroke = 0, size = 3) + 
    geom_smooth(method = "lm", se = FALSE, color = "red") + 
    scale_x_log10(label = scales::comma) +
    labs(title = "US County Populations verses Economic Connectedness 2018", subtitle = "Population size does not matter to EC", caption = "Opportunity Insights", x = "Population", y = "Economic Connectedness")
```

Plot 2: US County Population vs. Economic Connectedness (2018)
This scatterplot shows the relationship between county population size and economic connectedness (EC).

Each point represents a county.

The x-axis is log-scaled to account for the wide range of population sizes.

Points are styled in black with partial transparency (alpha = 0.3) to reduce overplotting.

A linear trendline is added in red (geom_smooth(method = "lm")) without the confidence interval shading (se = FALSE).

Interpretation:
The plot suggests that there is little to no strong linear relationship between a county’s population and its level of economic connectedness. The red trendline appears relatively flat, supporting the subtitle’s claim that population size does not matter to EC.
